Binary companions of red giant stars with APOGEE: \\ catalog and companions that survive the common envelope

### 2017-12-14 paper/1-catalog/twoface-catalog.tex
change subscripting

\title{Binary companions of red giant stars with APOGEE I: \\
       catalog and companions that survive the common envelope}

@@

\todo{An alternate approach to this intro is to start with an overview of
      binary stars, radial velocity measurements of binarity in general...}

\todo{As is, the intro is missing many citations}

Time-domain radial-velocity measurements of stars contain information about
massive companions: even with two successive observations of a single star, a
difference in the measured radial velocities implies the existence of at least
one companion.
However, with few or imprecise radial-velocity measurements, the orbital
properties of the companion(s) are very poorly constrained.
Most prior searches for companions using survey RV data have therefore
restricted their searches to only sources with many epochs, so that the orbital
solution can be unambiguously determined.
The vast majority of spectroscopic targets with repeat observations in the
largest (by number of objects) stellar spectroscopic surveys are in the opposite
regime: targets are often observed just a few times with sparse, non-uniform
phase coverage.

% With such data, even if the period or other generic orbital parameters
% are very poorly constrained, limits on companion mass or pericentric distance
% of the companion may still XX.

@@

\begin{eqnarray}
    p(D_n \given \alpha) &=& \int \dd \theta_n \, p(D_n \given \theta_n) \,
      p(\theta_n \given \alpha)\\
    &=& \int \dd \theta_n \, p(D_n \given \theta_n) \, p(\theta_n \given \alpha) \,
      \frac{p(\theta_n \given D_n, \alpha_0)}{p(\theta_n \given D_n, \alpha_0)}\\
    &=& \int \dd \theta_n \, p(D_n \given \theta_n) \, p(\theta_n \given \alpha) \,
      p(\theta_n \given D_n, \alpha_0) \,
      \frac{p(D_n \given \alpha_0)}{p(D_n \given \theta_n) \,
      p(\theta_n \given \alpha_0)}\\
    &=& p(D_n \given \alpha_0) \, \int \dd \theta_n \,
      \frac{p(\theta_n \given \alpha)}{p(\theta_n \given \alpha_0)} \,
      p(\theta_n \given D_n, \alpha_0)\\
    &\approx& \mathcal{Z}_n \, \frac{1}{K_n} \,
      \sum_k^{K_n} \frac{p(\theta_n^{(k)} \given \alpha)}{p(\theta_n^{(k)} \given \alpha_0)}\\
    &=& \frac{\mathcal{Z}_n}{K_n} \,
      \sum_k^{K_n} \frac{p(y_n^{(k)} \given \alpha)}{p(y_n^{(k)} \given \alpha_0)}
\end{eqnarray}

\begin{eqnarray}
    p(\{D_n\} \given \alpha) &\propto& \prod_n^N \frac{1}{K_n} \,
      \sum_k^{K_n} \frac{p(y_n^{(k)} \given \alpha)}{p(y_n^{(k)} \given \alpha_0)}\\
    \ln p(\{D_n\} \given \alpha) &\propto& \sum_n^N \left[
      \ln\left( \sum_k^{K_n} \frac{p(y_n^{(k)} \given \alpha)}{p(y_n^{(k)} \given \alpha_0)} \right)
      - \ln K_n\right]\\
    &\propto& \sum_n^N \left[
      \underset{k}{\rm logsumexp}\left[ \ln{p(y_n^{(k)} \given \alpha)} - \ln{p(y_n^{(k)} \given \alpha_0)} \right]
      - \ln K_n\right]
\end{eqnarray}

>>>>

\title{Binary companions of red giant stars with APOGEE: \\
       catalog and companions that survive the common envelope}

@@

\todo{Intro is missing many citations}

Nearly all stars form with stellar companions in multiplets or clusters, through
subsequent dynamical evolution that stars may lose their neighbors.
Main sequence stars in the solar neighborhood more often appear in binary or
multiple star systems than singles (\citealt{ragavhan,tokovinin,todo}).
- Related to fragmentation in collapsing protostellar / molecular cloud ->
  multiple stars (e.g., \citealt{Raskutti:2016})
- Population of stellar binaries and multiplets -> information about star
  formation, dynamics

Even without stellar or sub-stellar companions, single stars likely have
planetary-mass companions (\citealt{todo}.
- Different formation channel for planets?
- Sub-stellar companions?

- Almost all stars have companions of some mass
These systems have a large dynamic range of constituent and orbital
characteristics.
For example, for binary main-sequence stars, mass-ratios span from XX to 1 and
periods from XX to YY years.
- Population of companions and trends (e.g., with metallicity) -> star and
  planet formation processes

- Expect differences in evolved star pop. from main sequence populations:
  - mass loss
  - envelope -> engulfment?
- But less is known about the population of companions to evolved stars.
- Current samples limited in dynamical range of chemical properties, location,
  age (local to sun)
- Brighter, but typically larger distances, direct imaging not feasible
- Eclipsing companions good, but low mass companions stars -> hard to find
  (giants are big)
- Need large sample of stars with time-domain spectroscopy

Time-domain radial-velocity measurements of stars contain information about
massive companions: even with two successive observations of a single star, a
difference in the measured radial velocities implies the existence of at least
one companion.
However, with few or imprecise radial-velocity measurements, the orbital
properties of the companion(s) are very poorly constrained (e.g.,
\citealt{Price-Whelan:2017}).
The vast majority of spectroscopic targets with repeat observations in the
largest (by number of objects) stellar spectroscopic surveys are often observed
just a few times with sparse, non-uniform phase coverage.
Most prior searches for companions using survey RV data have therefore
restricted their searches to only sources with many, high-precision epochs, so
that the orbital solution can be unambiguously determined (e.g.,
\citealt{Troup:2016}), or have used simple statistics computed from the data to
study multiplicity (e.g., ${\rm RV}_{\rm max} - {\rm RV}_{\rm min}$;
\citealt{Badenes:2017}).

@@

\begin{eqnarray}
    p(D_n \given \alpha) &=& \int \dd \theta_n \, p(D_n \given \theta_n) \,
      p(\theta_n \given \alpha)\\
    &=& \int \dd \theta_n \, p(D_n \given \theta_n) \, p(\theta_n \given \alpha) \,
      \frac{p(\theta_n \given D_n, \alpha_0)}{p(\theta_n \given D_n, \alpha_0)}\\
    &=& \int \dd \theta_n \, p(D_n \given \theta_n) \, p(\theta_n \given \alpha) \,
      p(\theta_n \given D_n, \alpha_0) \,
      \frac{p(D_n \given \alpha_0)}{p(D_n \given \theta_n) \,
      p(\theta_n \given \alpha_0)}\\
    &=& p(D_n \given \alpha_0) \, \int \dd \theta_n \,
      \frac{p(\theta_n \given \alpha)}{p(\theta_n \given \alpha_0)} \,
      p(\theta_n \given D_n, \alpha_0)\\
    &\approx& \mathcal{Z}_n \, \frac{1}{K_n} \,
      \sum_k^{K_n} \frac{p(\theta_{nk} \given \alpha)}{p(\theta_{nk} \given \alpha_0)}\\
    &=& \frac{\mathcal{Z}_n}{K_n} \,
      \sum_k^{K_n} \frac{p(y_{nk} \given \alpha)}{p(y_{nk} \given \alpha_0)}
\end{eqnarray}

\begin{eqnarray}
    p(\{D_n\} \given \alpha) &\propto& \prod_n^N \frac{1}{K_n} \,
      \sum_k^{K_n} \frac{p(y_{nk} \given \alpha)}{p(y_{nk} \given \alpha_0)}\\
    \ln p(\{D_n\} \given \alpha) &\propto& \sum_n^N \left[
      \ln\left( \sum_k^{K_n} \frac{p(y_{nk} \given \alpha)}{p(y_{nk} \given \alpha_0)} \right)
      - \ln K_n\right]\\
    &\propto& \sum_n^N \left[
      \underset{k}{\rm logsumexp}\left[ \ln{p(y_{nk} \given \alpha)} - \ln{p(y_{nk} \given \alpha_0)} \right]
      - \ln K_n\right]
\end{eqnarray}
